LACRE 2022: abstract

### 2022-01-04 presentations/2022-01-25_lacre/2022-01-25_lacre-abstract.Rmd
Update participants

Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language [e.g., @costa2000cognate; @thierry2007brain]. It has been suggested that this parallel activation is already present during toddlerhood [e.g., @von2012language; @jardak2019labels], but it is unclear how this parallel activation impacts the developing lexicon. We tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task. Participants were tested exclusively in their language of most exposure. two pictures were presented side-by-side, one of them was named, and participants' visual preference for the named (target) picture was taken as a proxy of word recognition. Each pair of pictures was preceded by the presentation of a silent image (prime). We manipulated two variables regarding to the relationship between the label associated to the prime image and the target word: their phonological overlap in the testing language and the cognate status of the prime label. This resulted in three types of trials: trials in which prime and target labels shared phonological onset and the prime label was a cognate (cognate trials; e.g., *flower*/*flor*-*bird*, for an English-Spanish participant), trials where prime and target labels shared phonological onset but the prime label was a non-cognate (non-cognate trials; e.g., *chair*/*silla*-*bird*), and trials where prime and target labels did not share phonological onset (unrelated trials; *car*/*coche*-*bird*).

>>>>

Previous studies have provided evidence that bilingual lexical access is language non-selective: recognising and producing words in one language activates lexical representations of words in the other language [e.g., @costa2000cognate; @thierry2007brain]. It has been suggested that this parallel activation is already present during toddlerhood [e.g., @von2012language; @jardak2019labels], but it is unclear how this it impacts the developing lexicon. We tested Catalan-Spanish bilinguals in a primed word recognition task, in which the auditory stimuli presented during the task were exclusively in participants' dominant language. We registered participants' looking preference for named (target) pictures as an indicator of word recognition. In primed trials, target pictures were preceded by the presentation of a silent picture whose label shared phonological onset with the target label. In non-primed trials, both labels had different onsets. We also manipulated the cognate status of the prime labels: some prime labels also shared phonological onset with their translation in participants' other language, while others did not. This resulted in three types of trials: trials in which prime and target labels shared phonological onset and the prime label was a cognate (cognate trials; e.g., *flower*/*flor*-*bird*, for an English-Spanish participant), trials where prime and target labels shared phonological onset but the prime label was a non-cognate (non-cognate trials; e.g., *chair*/*silla*-*bird*), and trials where prime and target labels did not share phonological onset (unrelated trials; *car*/*coche*-*bird*).
